%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Siddarth Sreeni 
%

%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Siddarth}{Sreeni}{ 
\href{mailto:sidda2158@gmail.com}{sidda2158@gmail.com} | +91-9400502158
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{BITS-Pilani}
\descript{B.E(honors) in Electrical and Electronics Engineering}
\location{Grad. 2018 | $7.3$}
\sectionsep

\subsection{Vijayagiri Public School}
\descript{Senior High School}
\location{Grad. May 2014  | $94.0$}
\sectionsep

\subsection{Toc-H Public School}
\descript{High School}
\location{Grad. May 2012 | $9.6$}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
LinkedIn://  \href{https://www.linkedin.com/in/siddarth-sreeni/}{\custombold{siddarth-sreeni}} \\
StackOverflow:// \href{https://stackoverflow.com/users/5801823/siddarth-sreeni}{\custombold{siddarth-sreeni}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Expertise}
\subsection{Technologies Used/Worked On}
Amazon Web Services \\
DevOps\\
Application design and development\\
NoSQL - DynamoDB, Cassandra \\
RDBMS - Oracle DBMS, PostGreSQL \\
Micro-services \\
Artificial Intelligence \\
Cloud Computing

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\textbullet{} Dockers \textbullet{} Apache Ignite \textbullet{} Apache Spark \\
\textbullet{} Kubernetes \textbullet{} DCOS, Mesos \textbullet{}  ECR\\
\textbullet{} Fargate \textbullet{} AWS Lambda, SQS \textbullet{} SNS \\
\textbullet{} DAX \textbullet{} Android \textbullet{} C \textbullet{} Linux \\
\textbullet{} Distributed Data \textbullet{} Shell scripting \\
\textbullet{} scala \textbullet{} python \textbullet{} SQL \\ 
\textbullet{} C++ \textbullet{} Java \textbullet{} Git \textbullet{} Jenkins\\
\textbullet{} EC2 \textbullet{} AWS dynamoDB \textbullet{} Open Source 
\sectionsep


\section{interests} 

\textbullet{} Reading \textbullet{} Travelling \\
\textbullet{} Tech savvying\\
\textbullet{} Sports e.g. Basket Bakk, Football\\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{HERE Technologies / Nokia HERE MAPS}

\descript{Software Engineer II, Mumbai }
\location{July 2018 – Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Pioneered a drastic change to micro-services architecture from the existing relational model. Part of the driving team that initiated the changed of the decade old legacy systems and software.
\item Successfully worked on enhancing the API-services, Production support and also worked on state of the art technology mostly on AWS.
\item Proficient in legacy software codes and part of the team that is charge of the major transition. 
\end{tightemize}

\descript{R\&D Research Intern, Mumbai }
\location{Jan 2018 – June 2018}
\begin{tightemize}\item Worked on a POC on AWS using fargate to replace CONTROL-M; a job scheduling which later went onto be showcased in engineering show case. Earned learn fast and win-together appreciations from leader ship
\item Re-wrote the house number location prediction using machine learning and analysed the problem statement. Currently in production environment.
\item Worked on the initial framework and successfully converted a tightly coupled RDBMS data structure to NoSQL.
\end{tightemize}
\sectionsep

\sectionsep

\runsubsection{K.S.E.D.C, Gov.t of Kerala}

\descript{ Research Intern }
\location{July 2016 – Aug 2017 | Trivandrum, Kerala}
\begin{tightemize}\item Implementation of an Echo sounder on Open Source Hardware- (ARM 64 based processor) and software platforms.
\item Designed a Software for mapping the depth of the ocean floor logging data and plotting it in real time as used in the Indian Navy Ships and Vehicles.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{IOT in TinyOS}
\location{Jan-May 2016 |  BITS Pilani}
Used Telosb Motes to communicate with each other and send data to and fro across the internet
Mentor: Dr. Anupama K.R
\sectionsep

\runsubsection{Image processing using Machine Learning}
\location{Aug–Dec 2016 | BITS Pilani}
A comparison based study of classifying different 3D scan medical images (MRI) using different ML algorithms in Cuda.
Mentor: Dr. Anita Aggrawal.
\sectionsep

\runsubsection{Maritime data gathering and statistical analysis.}
\location{Oct2017–Mar 2018 | BITS Pilani}
Maritime data gathering and statistical analysis.
Mentor . Dr. R. P. Pradhan.
\sectionsep

\runsubsection{GPU Governor for SD820 SOC- Adreno 530}
\location{May 2017}
•Similar to on-demand but less intense than MSM-Adreno from Qualcomm 
•Graceful scaling of GPU frequency covering all frequency unlike performance mode 
\sectionsep
\end{minipage} 
\subsection{}{Publications} 
\begin{tightemize} \item Siddarth Sreeni., Hari S R., Harikrishnan R., Sreejith V., "Multi-Modal Posture Recognition System for Healthcare Applications" IEEE TENCON, South Korea, Oct 2018\\
\item Siddarth Sreeni., Sahitya Tahiliani., Tushar Gothankar., "Machine Learning Based Maximum Power Point Tracking In Tidal/Ocean Energy Conversion Systems" - International Journal  of Electronics, Electrical and Data Communication ,Volume 5 Issue 4
\end{tightemize}

\end{document}